Declarative Methods Term Project: \\ JumanG

### 2013-05-03 doc/paper.tex
paper so far. added a couple of comments

\subsubsection{Radial Solver}
Radial displays have been used for some time to display trees of various data in a way different from the typical top-down approach.
Introduced in 1992 by Eades (EADES CITATION), this layout lays the branches out circularly around the root branching outwards, drawing 
nodes at different radii from the center. We implemented our own radial solver that uses slightly different techniques than the original
method. We wrote our solver to evenly distribute nodes around the root at each level, rather than using the traditional style of weighting 
them based on the number of subnodes as is typical for a solver like this. We also chose to display nodes at their closest level to root. 
This allows the solver to draw non-tree graphs fairly well; better, in fact, than Graphviz's twopi on these graphs (INSERT COMPARISON GRAPHS) 
In general, a radial solver is better than a standard layered solver for drawing graphs that are relatively wider than they are deep. Our metric 
for determining whether the radial solver should be used is given by a measure of width, number of nodes / depth of the graph (put in math eq?) (Juneki
add more metanalysis here) (Insert some results here)

In addition to the use as an arrangement for directed graphs, we also found that the radial solver worked as an excellent way to presort nodes for the
Springs Solver, as it spreads the nodes out enough that the nodes resist clumping together.

\subsubsection{Springs Solver}
citation for the springs\cite{springs}
The springs algorithm, as outlined by (citation), computes a layout for a graph by approximating physics; all nodes repel each and every other node, 
and edges act as springs to hold the nodes together. This requires deriving values for these forces, as more highly connected graphs will have 
more edges, and thus more springs, throwing off the balance between the two forces that allows them to be spaced apart. In our solver, we decided
the best way to do this was to hold the spring factor constant and to adjust the repulsion force to generate graphs of desired size. After much 
experimentation, we determined that the equation to describe the force to be (math eq of total number of edges / total number of nodes +2 to the 3 /distance tithe 2)
The spring function was held to simply the distance between the two objects, emulating a spring with a spring constant of 1. We then applied these forces
to the nodes in the graph, keeping the result with the minimum total force in the system.

>>>>

\subsubsection{Radial Solver}
Radial displays have been used for some time to display trees of various data in a way different from the typical top-down approach.
Introduced in 1992 by Eades (EADES CITATION), this layout lays the branches out circularly around the root branching outwards, drawing 
nodes at different radii from the center. We implemented our own radial solver that uses slightly different techniques than the original
method. We wrote our solver to evenly distribute nodes around the root at each level, rather than using the traditional style of weighting 
them based on the number of subnodes as is typical for a solver like this. We also chose to display nodes at their closest level to root. 
This allows the solver to draw non-tree graphs fairly well; better, in fact, than Graphviz's twopi on these graphs 
%TODO (INSERT COMPARISON GRAPHS) 
In general, a radial solver is better than a standard layered solver for drawing graphs that are relatively wider than they are deep. Our metric 
for determining whether the radial solver should be used is given by a measure of width: 
$$\frac{number_{nodes}}{depth_{graph}}$$

%TODO add more metanalysis here) (Insert some results here)

In addition to the use as an arrangement for directed graphs, we also found that the radial solver worked as an excellent way to presort nodes for the Springs Solver, because it spreads the nodes out, preventing nodes from clumping together.

\subsubsection{Springs Solver}
%TODO
citation for the springs\cite{springs}

The springs algorithm, as outlined by (citation), computes a layout for a graph by approximating physics; all nodes repel each and every other node, 
and edges act as springs to hold the nodes together. This requires deriving values for these forces, as more highly connected graphs will have 
more edges, and thus more springs, throwing off the balance between the two forces that allows them to be spaced apart. In our solver, we decided
the best way to do this was to hold the spring factor constant and to adjust the repulsion force to generate graphs of desired size. After some 
experimentation, we used this equation to describe the force: 
%$$ \frac{number_{edges}}{number_{nodes}^{3}} $$
%(math eq of total number of edges / total number of nodes +2 to the 3 /distance tithe 2)

The spring function was held to simply the distance between the two objects, emulating a spring with a spring constant of 1. We then applied these forces
to the nodes in the graph, keeping the result with the minimum total force in the system.
